### 2018-02-05 README.rmd
organize pkgdown reference
use scale_x_discrete for categorical axis set

@@

This is a [**ggplot2** extension](http://www.ggplot2-exts.org/) for alluvial diagrams. The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is derived mostly from the [**alluvial**](https://github.com/mbojan/alluvial) package, but the **ggplot2** framework induced several conspicuous differences:

@@

```{r eval=TRUE}
titanic_wide <- data.frame(Titanic)
head(titanic_wide)
ggplot(data = titanic_wide,
       aes(axis1 = Class, axis2 = Sex, axis3 = Age,
           weight = Freq)) +
  scale_x_continuous(breaks = 1:3, labels = c("Class", "Sex", "Age")) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum", label.strata = TRUE) +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

>>>>

<!--
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
-->

This is a [**ggplot2** extension](http://www.ggplot2-exts.org/) for alluvial diagrams.

@@

The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is derived mostly from the [**alluvial**](https://github.com/mbojan/alluvial) package, but the **ggplot2** framework induced several conspicuous differences:

@@

```{r eval=TRUE}
titanic_wide <- data.frame(Titanic)
head(titanic_wide)
ggplot(data = titanic_wide,
       aes(axis1 = Class, axis2 = Sex, axis3 = Age,
           weight = Freq)) +
  scale_x_discrete(limits = c("Class", "Sex", "Age")) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum", label.strata = TRUE) +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```
